---
title: "p8105 Homework 6"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(mgcv)
library(modelr)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


### Problem 2

```{r}
homicide_data = read_csv("./data/homicide_data.csv")
```

* Create a `city_state` variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom `victim_race` is `white` or `black`. Be sure that `victim_age` is numeric.

```{r}
homicide = homicide_data %>% 
  mutate(
    city_state = str_c(city, ', ', state),
    solved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), FALSE, TRUE),
    victim_age = as.numeric(victim_age)
  ) %>% 
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
    victim_race %in% c("White", "Black")
    )
```

* For the city of Baltimore, MD, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of `glm` as an R object; apply the `broom::tidy` to this object; and obtain the estimate and confidence interval of the adjusted **odds ratio** for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_df = 
  homicide %>% 
  filter(city == "Baltimore")

bal_logistic = 
  baltimore_df %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy()

bal_logistic

bal_logistic %>% 
  mutate(
    OR = exp(estimate),
    conf_low = exp(estimate - 1.96 * std.error),
    conf_high = exp(estimate + 1.96 * std.error)) %>%
  select(term, Log_OR = estimate, OR, conf_low, conf_high) %>% 
  filter(term == "victim_sexMale") %>% 
  knitr::kable(digits = 3)
```

The output of `glm` was saved as `bal_logistic`. As shown in the output, for solving homicides comparing male victims to female victims keeping all other variables fixed, the estimate adjusted OR is 0.426, and confidence interval of the adjusted OR is (0.325, 0.558).

* Now run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of `purrr::map`, list columns, and `unnest` as necessary to create a dataframe with estimated ORs and CIs for each city.

Firstly, write a function:

```{r}
city_logistic = function(df) {
  
    glm(solved ~ victim_age + victim_sex + victim_race, data = df, family = binomial()) %>% 
    broom::tidy() %>% 
    mutate(
      OR = exp(estimate),
      conf_low = exp(estimate - 1.96 * std.error),
      conf_high = exp(estimate + 1.96 * std.error)) %>%
    select(term, Log_OR = estimate, OR, conf_low, conf_high)
  
}
```

Apply this function to the `homicide` dataframe:

```{r}
cities_logistic = 
  homicide %>% 
  filter(victim_sex %in% c("Female", "Male")) %>% 
  nest(df = -city_state) %>% 
  mutate(
    outcome = map(df, city_logistic)
  ) %>% 
  unnest(outcome) %>% 
  select(-df) %>% 
  filter(term == "victim_sexMale")
```

Here is the dataframe with estimated adjusted ORs and CIs for each city for solving homicides comparing male victims to female victims.

```{r}
cities_logistic %>% 
  knitr::kable(digits = 3)
```

* Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
cities_logistic %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(
      angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Estimated ORs and CIs for Each City",
    x = "City",
    y = "Estimated OR and CI"
  )
```

According to this plot, NYC has the lowest estimated adjusted OR for solving homicides comparing male victims to female victims, and Albuquerque has the highest. The majority of cities have ORs that are lower than 1, while a lot of them have CIs crossing the null value 1.


### Problem 3

* Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight = read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex, levels=c(1, 2), labels = c('Male','Female')),
    frace = factor(frace, levels=c(1, 2, 3, 4, 8, 9), labels = c('White','Black','Asian','Puerto Rican','Other','Unknown')),
    malform = factor(malform, levels=c(0, 1), labels = c('absent','present')),
    mrace = factor(mrace, levels=c(1, 2, 3, 4, 8), labels = c('White','Black','Asian','Puerto Rican','Other'))
  )

birthweight %>% drop_na()
```

Four categorical variables `babysex`, `frace`, `malform`, and `mrace` are converted to factor. And the number of rows is always why 4342 whether `drop_na` works or not. We can tell there is no missing value in this dataset.

* Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use `add_predictions` and `add_residuals` in making this plot.

We are interested in the association between baby’s length at birth and baby birth weight. Firstly, make a sctterplot between these two:

```{r}
birthweight %>% 
  ggplot(aes(x = blength, y = bwt)) + 
  geom_point(alpha = .3)
```

We a tell an approximately linear relationship between length and weight. Then, try to build a linear regression model:

```{r}
lmodel_a = lm(bwt ~ blength, data = birthweight)

lmodel_a %>% 
  broom::tidy()

birthweight %>% 
  add_predictions(lmodel_a) %>% 
  ggplot(aes(x = blength, y = bwt)) + 
  geom_point(alpha = .3) + 
  geom_line(aes(y = pred), color = "red")
```

Show a plot of model residuals against fitted values:

```{r}
birthweight %>% 
  add_predictions(lmodel_a) %>% 
  add_residuals(lmodel_a) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = .3) +
  labs(
    title = "Plot of Model Residuals against Fitted Values",
    x = "Fitted Value",
    y = "Residual"
  )
```

The plot implies heteroscedasticity problem -- it seems the residuals and the fitted values are correlated.

* Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only).

```{r}
lmodel_b = lm(bwt ~ blength + gaweeks, data = birthweight)

lmodel_b %>% 
  broom::tidy()
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between these.

```{r}
lmodel_c = lm(bwt ~ bhead * blength * babysex, data = birthweight)

lmodel_c %>% 
  broom::tidy()
```

* Make this comparison in terms of the cross-validated prediction error; use `crossv_mc` and functions in `purrr` as appropriate.

```{r}
cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
  )
  
cv_df = 
  cv_df %>% 
  mutate(
    lmodel_a_fits = map(.x = train, ~lm(bwt ~ blength, data = .x)),
    lmodel_b_fits = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    lmodel_c_fits = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_a_lm = map2_dbl(.x = lmodel_a_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_b_lm = map2_dbl(.x = lmodel_b_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_c_lm = map2_dbl(.x = lmodel_c_fits, .y = test, ~rmse(model = .x, data = .y))
  )
```

Look at the results by making box plots:

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot() +
  labs(
    title = "Box Plots of RMSEs for Three Model",
    x = "Model",
    y = "RMSE"
  )
```

According to the result, obviously, the third model (one using head circumference, length, sex, and all interactions) has the smallest RMSE.
